Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-12-08 doc/JFLA2022/Slides/Slides.tex
a few more slides

@@

  \begin{block}{Addition chains}
    \begin{itemize}
    \item    \textcolor{mathcolor}{algorithmics},
       \textcolor{mathcolor}{arithmetic},
  \item 
    \textcolor{coqstylecolor}{monadic notations},
    \textcolor{coqstylecolor}{PHOAS},
  \textcolor{coqstylecolor}{parametricity}, etc.
    \item
      \textcolor{plugincolor}{paramcoq (Chantal Keller, Marc Lasson)} 
          \end{itemize}
  \end{block}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
  \frametitle{Tests with Alectryon(1)}
  \begin{footnotesize}
      \inputsnippets{Schutte_Ex42a}   
      \inputsnippets{Schutte_Ex42b, Schutte_Ex42c}   
    \end{footnotesize}
  \end{frame}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{frame}[fragile]
    \frametitle{Tests with Alectryon(2)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Introduction}
  \begin{block}{}
We show a small but non-trivial example of using Alectryon
for writing a documentation (in pdf) of a proof written in Coq.    
  \end{block}

>>>>

\usepackage{tikz}
\usepackage{tikzsymbols}
\usepackage{pifont}
\usetikzlibrary{arrows}

@@

  \begin{block}{Addition chains}
    \begin{itemize}
    \item    \textcolor{mathcolor}{algorithmics},
       \textcolor{mathcolor}{arithmetic},
  \item 
    \textcolor{coqstylecolor}{monadic notations},
    \textcolor{coqstylecolor}{PHOAS},
  \textcolor{coqstylecolor}{parametricity}, etc.
    \item
      \textcolor{plugincolor}{paramcoq (Chantal Keller, Marc Lasson)} 
          \end{itemize}
  \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \TODO{}{Chose an example: for instance the length of hydra-battles: how we use \texttt{equations}, \texttt{ackermann}.
    Connexion with gaia (or potentially Minki's ordinals)
    (several slides).}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}

  \begin{figure}[h]
  \centering
  \begin{tikzpicture}[very thick, scale=0.3]
  \node (h1) at (4,0){$\bullet$};
  \node[blue] (h2) at (4,2){$\bullet$};
  \node[blue] (h3) at (2,4){$\bullet$};
  \node[blue] (h4) at (0,6){$\bullet$};
  \node[red!90!black] (h7) at (6,2){$\bullet$};
  \node[blue] (h5) at (4,6){$\bullet$};
  \node[blue] (h6) at (6,4){$\bullet$};
  \draw (h1) -- (h2) ;
  \draw (h2) -- (h3) ;
  \draw (h1) -- node[red!90!black,font=\small,sloped,shift={(0.01,-0.075)},rotate=90]{\textbf{\ding{34}}} (h7);
  \draw (h3) -- (h4) ;
  \draw (h3) -- (h5) ;
  \draw (h2) -- (h6);

  \node (h11) at (14,0){$\bullet$};
  \node[blue] (h12) at (14,2){$\bullet$};
  \node[blue] (h13) at (12,4){$\bullet$};
  \node[blue] (h14) at (10,6){$\bullet$};
  \node[blue] (h15) at (14,6){$\bullet$};
  \node[red!90!black] (h16) at (16,4){$\bullet$};
  \draw (h11) -- (h12) ;
  \draw (h12) -- (h13) ;
  \draw (h12) -- node[red!90!black,font=\small,sloped,shift={(0.01,-0.075)},rotate=90]{\textbf{\ding{34}}} (h16);
  \draw (h13) -- (h14) ;
  \draw (h13) -- (h15) ;

\node (hn1) at (24,0){$\bullet$};
\node[blue] (hn2) at (22,2) {$\bullet$};
\node[blue] (hn3) at (22,4) {$\bullet$};
\node[blue] (hn4) at (20,6){$\bullet$};
  \node[blue] (hn5) at (22,6){$\bullet$};
  \draw (hn1) -- (hn2) ;
  \draw (hn2) -- (hn3) ;
  \draw (hn3) -- (hn4) ;
  \draw (hn3) -- (hn5) ;
\node [blue](hn2b) at (24,2) {$\bullet$};
\node[blue] (hn3b) at (24,4) {$\bullet$};
\node [blue](hn4b) at (23.4,6){$\bullet$};
  \node [blue](hn5b) at (24.6,6){$\bullet$};
  \draw (hn1) -- (hn2b) ;
  \draw (hn2b) -- (hn3b) ;
  \draw (hn3b) -- (hn4b) ;
  \draw (hn3b) -- (hn5b) ;
  \node [blue](hn2c) at (26,2) {$\bullet$};
\node [blue](hn3c) at (26,4) {$\bullet$};
\node [blue](hn4c) at (26,6){$\bullet$};
  \node [red!90!black] (hn5c) at (28,6){$\bullet$};
  \draw (hn1) -- (hn2c) ;
  \draw (hn2c) -- (hn3c) ;
  \draw (hn3c) -- (hn4c) ;
  \draw (hn3c) -- node[red!90!black,font=\small,sloped,shift={(0.01,-0.075)},rotate=90]{\textbf{\ding{34}}} (hn5c) ;
\end{tikzpicture}

\caption{Three successive states of a hydra in a battle,
at time $t=0,1,2$}
  \label{fig:round}
\end{figure}

\begin{figure}[h]
  \centering

\begin{tikzpicture}[very thick, scale=0.3]
\node (hn1) at (4,0){$\bullet$};
\node[blue] (hn2) at (2,2) {$\bullet$};
\node[blue] (hn3) at (2,4) {$\bullet$};
\node[blue] (hn4) at (0,6){$\bullet$};
  \node[blue] (hn5) at (2,6){$\bullet$};
  \draw (hn1) -- (hn2) ;
  \draw (hn2) -- (hn3) ;
  \draw (hn3) -- (hn4) ;
  \draw (hn3) -- (hn5) ;
\node [blue](hn2b) at (4,2) {$\bullet$};
\node [blue](hn3b) at (4,4) {$\bullet$};
\node [blue](hn4b) at (3.4,6){$\bullet$};
  \node [blue] (hn5b) at (4.6,6){$\bullet$};
  \draw (hn1) -- (hn2b) ;
  \draw (hn2b) -- (hn3b) ;
  \draw (hn3b) -- (hn4b) ;
  \draw (hn3b) -- (hn5b) ;
  \node [blue](hn2c) at (6,2) {$\bullet$};
\node [blue](hn3c) at (6,4) {$\bullet$};
\node [blue](hn4c) at (6,6){$\bullet$};
 % \node (hn5c) at (8,6){$\bullet$};
  \draw (hn1) -- (hn2c) ;
  \draw (hn2c) -- (hn3c) ;
  \draw (hn3c) -- (hn4c) ;
  % \draw (hn3c) -- (hn5c) ;
  \node [blue](hn3d) at (8,4) {$\bullet$};
  \draw (hn2c) -- (hn3d) ;
  \node [blue](hn4d) at (8,6) {$\bullet$};
  \draw (hn3d) -- (hn4d) ;

 \node [blue](hn3e) at (10,4) {$\bullet$};
  \draw (hn2c) -- (hn3e) ;
  \node [blue](hn4e) at (10,6) {$\bullet$};
  \draw (hn3e) -- (hn4e) ;

  \node [blue](hn3f) at (12,4) {$\bullet$};
  \draw (hn2c) -- (hn3f) ;
  \node [red!90!black](hn4f) at (12,6) {$\bullet$};
  \draw (hn3f) -- node[red!90!black,font=\small,sloped,shift={(0.01,-0.075)},rotate=90]{\textbf{\ding{34}}} (hn4f) ;

  \node at (16,0) {$\dots$} ;

 \node [black](hn4h) at (21,0) {$\bullet$};
\node [red!90!black](hn4g) at (21,2) {$\bullet$};
   \draw (hn4h) -- node[red!90!black,font=\small,sloped,shift={(0.01,-0.075)},rotate=90]{\textbf{\ding{34}}} (hn4g) ;

  \node [black](hn4f) at (24,0) {$\bullet$};
\end{tikzpicture}
 \caption{At $t=3,\dots,x^?-1,x^?$}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \TODO{}{maintenance, CI/CD,  etc.   (several slides).}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \TODO{}{Alectryon (several slides)}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
  \frametitle{Tests with Alectryon(1)}
  \begin{footnotesize}
      \inputsnippets{Schutte_Ex42a}   
      \inputsnippets{Schutte_Ex42b, Schutte_Ex42c}   
    \end{footnotesize}
  \end{frame}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{frame}[fragile]
    \frametitle{Tests with Alectryon(2)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Old stuff

\begin{frame}
  \frametitle{Introduction}
  \begin{block}{}
We show a small but non-trivial example of using Alectryon
for writing a documentation (in pdf) of a proof written in Coq.    
  \end{block}
